Equalizer: A Mature Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Fill in some equalizers
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@6 db7c848b-7755-4df2-b763-8796797afa52

\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{times}
%\usepackage{tabularx}
\usepackage{amsmath}
%\usepackage{url}
\usepackage{subfigure}
\usepackage{multirow}

@@

@@

Time-multiplexing, or DPlex, was already implemented in \cite{BRE:05}. While it
increases the framerate linearly, it does not decrease the latency between user
input and the corresponding output. Consequently, this decomposition mode is
mostly useful for non-interactive movie generation. It is transparent to
Equalizer applications, but does require the configuration latency to be equal
or greater than the number of source channels. Furthermore, to work in a
multi-threaded, multi-GPU configuration, the application needs to support
running the rendering threads asynchronously, as outlined in
\sref{SEC_threading}.

@@

reactive load equalization, describe tunables (damping, resistance, delta,
granularity), sort-first respects input channel size

\subsubsection{Cross-Segment Load Equalizer}

summarize \cite{EEP:11}

@@

\subsubsection{Frame Rate Equalizer}

>>>>

\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{times}
%\usepackage{tabularx}
\usepackage{amsmath}
%\usepackage{url}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{paralist}

@@

Virtual Reality

\subsection{Head Tracking}

@@

Time-multiplexing, or DPlex, was already implemented in \cite{BRE:05}. While it
increases the framerate linearly, it does not decrease the latency between user
input and the corresponding output. Consequently, this decomposition mode is
mostly useful for non-interactive movie generation. It is transparent to
Equalizer applications, but does require the configuration latency to be equal
or greater than the number of source channels. Furthermore, to work in a
multi-threaded, multi-GPU configuration, the application needs to support
running the rendering threads asynchronously, as outlined in
\sref{SEC_threading}. The output frame rate of the destination channel is
smoothened using a frame rate equalizer (\sref{SEC_framerateEq}).

@@

Sort-first and sort-last load balancing is the most obvious optimization for
these parallel rendering modes. Our load equalizer is fully transparent for
application developers, that is, it uses a reactive approach based on past
rendering times. This assumes a reasonable frame-to-frame coherency. Our
implementation stores a 2D or 1D grid of the load, mapping the load of each
channel. The load is stored in normalized 2D/1D coordinates using
$\frac{time}{area}$ as the load, the contributing source channels are organized
in a binary tree, and then the algorithm balances the two branches of each level
by equalizing the integral over the area on each side.

We have implemented various tunable parameters allowing application developers
to optimize the load balancing based on the characteristics of their rendering
algorithm:
\begin{compactdesc}
\item[Damping] reduces frame-to-frame oscillations. It is a normalized scalar
  defining how much of the computed delta from the previous position is
  applied. The equal load distribution within the region of interest assumed by
  the load equalizer is in reality not equal, causing the load balancing to
  overshoot.
\item[Resistance] eliminates small deltas in the load balancing step. This might
  help the application to cache some computations since the frustum does not
  change each frame.
\item[Boundaries] define the modulo factor in pixels onto which a load split may
  fall. Some rendering algorithms produce artefacts related to the OpenGL raster
  position, e.g., screen door transparency, which can be eliminated by aligning
  the boundary to the pixel repetition. Furthermore, some rendering algorithms
  are sensitive to cache alignments, which can again be exploited by chosing the
  corresponding boundary.
\end{compactdesc}

\subsubsection{Cross-Segment Load Balancing}

Cross-segment load balancing addresses the optimal resource allocation of $n$
rendering resources to $m$ output channels (with $n\geq m$). The view equalizer
works in conjunction with load equalizer balancing the individual output
channels. It monitors the usage of shared source channels (across outputs) and
activates them to balance the rendering time of all outputs. In \cite{EEP:11},
we provide a detailed description and evaluation of our algorithm.

@@

\subsubsection{Frame Rate Equalizer}\label{SEC_framerateEq}
